
\documentclass[]{resume-openfont}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mahesh}{Maddhuru}
{ \urlstyle{same}
\href{mailto:mahesh21319@gmail.com}{mahesh21319@gmail.com} | 
+1 (304) 215-2613 | 
\href{https://mahesh-maddhuru.github.io/}{Personal Website} |
\href{http://www.linkedin.com/in/mahesh-m97}{LinkedIn} | 
\href{https://leetcode.com/mahm/}{Leetcode}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Virginia Tech}
\descript{MEng in Computer Science}
\location{May 2024 | Blacksburg, VA}
\sectionsep

\subsection{BMS}
\descript{College of Engineering}
\descript{BE in Computer Science}
\location{ GPA: 8.87 / 10}
\location{Grad. May 2019 | Bangalore, IN}
\sectionsep

\subsection{Vikaas}
\descript{High School}
\location{ Grade: 95.16\%}
\location{Grad. May 2015 |  Mangalore, IN}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Links} 
% Facebook:// \href{https://facebook/dd}{\bf dd} \\
% Github:// \href{https://github.com/deedydas}{\bf deedydas} \\
% LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\bf debarghyadas} \\
% YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\bf DeedyDash007} \\
% Twitter://  \href{https://twitter.com/debarghya_das}{\bf @debarghya\_das} \\
% Quora://  \href{https://www.quora.com/Debarghya-Das}{\bf Debarghya-Das}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Networks and Protocols \\
Network Security \\
Information Security \\
Blockchain \\
Machine Learning \\
Al Tools Software Development \\
\sectionsep

\subsection{Undergraduate}
Analysis and design of Algorithms \\
Operating Systems \\
Computer Networks \\
DBMS \\
Cryptography and Network Security \\
Web Development \\
Data Science \\
Discrete Mathematics \& Linear Algebra \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Java \textbullet{}   JavaScript \textbullet{} Python \textbullet{} C++ \\~\\
\subsection{Frameworks}
Dropwizard \textbullet{} Dagger 2.0 \textbullet{} SpringBoot \textbullet{} Terraform \textbullet{} Express JS \textbullet{} Android \textbullet{} Hibernate \textbullet{} JUnit \textbullet{} Mockito \textbullet{} Flask \textbullet{} Selenium \\~\\
\subsection{Databases}
Oracle DB \textbullet{} MongoDB \textbullet{} MySQL \\~\\ 
\subsection{Software Tools}
Oracle Cloud \textbullet{} CI/CD tools \textbullet{} DevOps \textbullet{} Docker \textbullet{} GIT \textbullet{} Maven \textbullet{} Gradle \\~\\ 
\subsection{Web Development}
VueJS \textbullet{}  AngularJS \textbullet{} JQuery \textbullet{} Bootstrap \textbullet{} D3.js \\~\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Oracle Cloud Infrastructure (OCI)}
\descript{| Member of Technical Staff IC2 (SDE-2) }
\location{October 2021 – December 2022 | Bangalore, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led and developed entire infrastructure for an emergent system to apply \textbf{quick patches to live hypervisors}.
\item Successfully navigated the project through the \textbf{CSSAP security review process}.
\item Redesigned and developed modules for Yum management, linux system file modification, custom package installation, and validations.
\item These Modules \textbf{optimized the 'image build pipeline'}, reducing build time by approximately 25\% and enhancing its stability.
\item Developed a versatile Maven plugin for parallel \textbf{Docker image retrieval} on all build hosts.
\item As the \textbf{Release coordinator}, deployed the updated Hypervisor base image on the Virtual Machine Infrastructure fleet.
\item As an \textbf{On-Call engineer}, successfully resolved a multitude of customer issues.
\end{tightemize}
\sectionsep

\runsubsection{Akamai}
\descript{| Software Engineer II + Software Engineer + Intern }
\location{January 2019 – September 2021 | Bangalore, IN}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and developed the \textbf{"Activation" algorithm}, reducing product operations team's efforts by 50\% through complex business logic computation (\textbf{calculating the product’s pricing} based on region, rate card, partner discount, etc.) and \textbf{automated product launch lifecycle} with smart retry mechanism.
\item \textbf{Developed Authorization layer} from the ground up with granular data access control.
\item Developed a \textbf{lock mechanism} to prevent product data changes in a non-draft state during configuration workflow.
\item Devised and \textbf{optimized partner open APIs} for fast reads (<1.5 seconds response time).
\item Improved response times for client APIs by implementing \textbf{inter-service calls and data caching}.
\item Facilitated integration of multiple client systems with our services.
\item Built many reusable \textbf{UI components on AngularJS} for configuring product metadata.
\end{tightemize}
\sectionsep

\runsubsection{Leanovate Solutions}
\descript{| Fullstack Engineer Intern }
\location{June 2018 - November 2018 | Bangalore, IN}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Assisted in designing a \textbf{MongoDB} database  for a building management system.
\item Developed \textbf{REST APIs in ExpressJS} to manage meeting room booking.
\item Devised automation tests in Python using \textbf{Selenium}.
\item  Generated PDF reports for booking statistics on a \textbf{Flask microservice}.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Powerchain}
\descript{| NodeJS, DatSwarm DHT | \href{https://github.com/mahesh-maddhuru/powerchain}{\faGithubSquare}}
% \location{January 2019 – May 2019 | Bangalore, IN}
% \item Light Weight, standard, and secure internetwork communication protocol for blockchain-based systems
A portable \textbf{blockchain system} that uses a custom protocol to enable \textbf{internetwork transactions} without middlemen and uses \textbf{custom packets} to reduce network congestion in blockchain-based systems.
% \item Provides a web login for users and CLI for miners participating in the network.
\sectionsep

\runsubsection{BMS.net}
\descript{| Android, Firebase, Google Map API}
% \location{January 2018 – May 2018 | Bangalore, IN}
An Android social media app that lists and \textbf{notifies the university's circulars}, lists upcoming live events, \textbf{pins live events} like workshops, etc. on the university map, and features student community \textbf{group live chat}.
\sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2014	     & top 52/2500  & KPCB Engineering Fellow\\
% 2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
% 2013	     & National  & Jump Trading Challenge Finalist\\
% 2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
% 2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
% 2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
